CS378: Final Project - Data Artifacts \\ \url{https://github.com/sarimaleem/cs378_fp}

### 2023-04-25 paper/main.tex
some additions to performance analysis

As can be seen from the table,

>>>>

In general, the model seems to do well with Separating Entailment and
Contradiction. For example, it only incorrectly identifies 2.47\% of entailment
examples as contradiction and 2.37\% of contradiction examples as entailement.
However, the model struggles more to understand the relationship between,
entailment and neutral, as well as contradiction and neutral.
